On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-08 main.tex
Update main.tex
Bit operation cost, correction

\paragraph*{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
\begin{enumerate}
    \item We defined $S = \{1,2,\hdots,\lceil 3\epsilon^{-1}3n^2(2d)^{3n} \rceil \}$
      and therefore the height of any $a_{i,j} \in S$ is at most
    \[
    \log 1/{\epsilon} + \log(3n^2(2d)^{2n}) \in O^{\sim}(n\log d + \log 1/{\epsilon}).
    \]
    \item As a result, by \cite[Lemma 1.2(1)(c)]{SharpEstimatesForTheEffectiveN}, all coefficients in 
      $f^\mA$ have height $ O^{\sim}(b + d\log 1 / \epsilon + dn)$.
    \item 
    After computing the partial derivatives, the height grows by at
    most another factor of $\log d$. Thus, all polynomials in the
    system considered at Step 3 have height $ O^{\sim}(b + d\log 1 /
    \epsilon + dn)$. All integer coefficients appearing in $\Gamma_i$ 
    satisfy the same bound.    
    %% Furthermore, preparing the
    %% straight line program for the gradient of $f$ does not introduce
    %% large integers. The integers in $\grad (f)$ are of the same
    %% magnitude as in $\Gamma$.
    \item As a result, after applying \cite[Algorithm 2]{SH} $k$ times
      for each index $i$, with $k = O(\log n + \log 1 / \epsilon)$,
      the total boolean cost of the algorithm is
      \[
      O^{\sim}(d^{3n+1}(\log1/\epsilon)(b + \log1/\epsilon))
      \]
      where the polynomials in the output have degree at most $d^n,$ and height at most
      \[
      O^{\sim}(d^{n+1}(b + \log 1 / \epsilon)).
  \]
\end{enumerate}

>>>>

\paragraph*{Bit operation cost:} The following lists the costs for each step of Algorithm 1:
\begin{enumerate}
    \item We defined $S := \{1,2,\hdots,\lceil 3\epsilon^{-1}6n^3(2d)^{2n} \rceil \}$
      and therefore the height of any $a_{i,j} \in S$ is at most
    \[
    \log 3/{\epsilon} + \log(6n^3(2d)^{2n}) \in O^{\sim}(\log 1/{\epsilon} + n\log d).
    \]
    \item 
    After computing the partial derivatives, the height grows by at
    most another factor of $\log d$. Thus, all polynomials in the
    system considered at Step 3 have height $ O^{\sim}(b + d\log 1 /
    \epsilon + dn)$. All integer coefficients appearing in $\Gamma_i$ 
    satisfy the same bound.    
    %% Furthermore, preparing the
    %% straight line program for the gradient of $f$ does not introduce
    %% large integers. The integers in $\grad (f)$ are of the same
    %% magnitude as in $\Gamma$.
    \item As a result, after applying \cite[Algorithm 2]{SH} $k$ times
      for each index $i$, with $k = O(\log n + \log 1 / \epsilon)$,
      the total boolean cost of the algorithm is
      \[
      O^{\sim}(d^{3n+1}(\log1/\epsilon)(b + \log1/\epsilon))
      \]
      where the polynomials in the output have degree at most $d^n,$ and height at most
      \[
      O^{\sim}(d^{n+1}(b + \log 1 / \epsilon)).
  \]
\end{enumerate}
